\chapter{Development tasks}
Given the design described in the previous chapter, we here define initial development tasks as well as an estimate of their size. 
Note: These are \emph{rough ballpark} estimates.




\section{Initial prototype}

\subsection*{UC1a: Sensor data from RabbitMQ}
\subsubsection{Task: Initial database}
Get PostgreSQL database up and running with core schema (possibly excluding prediction tables) using SQLAlchemy.

Estimate: 1 week


\subsubsection{Task: Data layer impl. for storing sensors and measurements}
Implementation in \texttt{DBProxy/DBAccess}

Estimate: 3 days


\subsubsection{Task: Initial version of Data Provider framework}
Implement an initial \texttt{DataProviderManager, DataProvider} and dummy \texttt{DataAdapter and DataInterpreter}.

Estimate: 3 days.

\subsubsection{Task: RabbitMQAdapter}
Implement \texttt{RabbitMQAdapter}.

Estimate: 4 days.

\subsubsection{Task: Interpret Grundfoss data}
Imlement interpretation of Grundfoss data from RabbitMQ. Store measurements in DB.

Estimate: 3 days.

\subsection*{UC1b: Develco sensor data from RabbitMQ}
\subsubsection{Task: Intepret Develco data}
Implement interpretation of Develco data from RabbitMQ. Store measurements in DB.

Estimate: 3 days.

\subsection*{UC2: Sensor and prediction data from FTP}
\subsubsection{Task: Database schema for predictions}
DB schema and access through \texttt{DBAccess}.

Estimate: 2 days.

\subsubsection{Task: Store DataProvider config}
It should be possible to configure multiple dataproviders and store the configuration. DB schema and access through data layer.

Estimate: 2 days.

\subsubsection{Task: FTPAdapter}
Implement an \texttt{FTPAdapter}. Store measurements and predictions in DB, avoiding duplication.

Estimate: 3 days.

\subsection*{UC3: Scheduled ControlAction is executed}
\subsubsection{Task: Initial version of Controller framework}
Initial \texttt{ControllerManager}, dummy \texttt{ControlStrategy, Controller}.

Estimate: 3 days.

\subsubsection{Task: VentilationControllerAdapter}
Communicate with ventilation system using HTTP.

Estimate: 3 days.

\subsubsection{Task: Execute scheduled action}
Read a scheduled action from DB and actuate ventilation controller.

Estimate: 2 days.

\subsection*{UC5: ControlStrategy schedules action(s)}
\subsubsection{Task: Simple ControlStrategy}
Simple \texttt{ControllerStrategy} which schedules ventilation system to run at lower setting at night.

Estimate: 2 days.


\section{Summary}
The above covers acquiring measurements from RabbitMQ, predictions and measurements from FTP and scheduling actions for controlling the ventilation system.

The estimates sum up to approx. 5 man-weeks. Taking unforseen complications into account, 6-8 weeks is probably more realistic. 
